Minimizing post-shock forecasting error through aggregation of outside information

### 2020-12-31 Revision/list.tex
revised comments and manuscript with addition of Section 5.2 for apple example

@@

\textbf{Summary of \cite{clements1996intercept}:} \cite{clements1996intercept} proposes three intercept correction for $m$-ahead forecasts of VECM. They are constant adjustment throughout the $m$ periods, a one-off adjustment, simple adjustment, and tailing-off forecast. In their setup, let $\hat{\boldsymbol{\varepsilon}}_{T}$ be the residual of VECM at $t= T$ and we are interested in  $m$-ahead forecasts. Denote the $m$-ahead forecasts by $\hat{y}_{ T+ m}$ and the adjusted forecasts by $\hat{\boldsymbol{y}}_{T+m}^*$. The \emph{constant adjustment}  considers $\hat{\boldsymbol{y}}_{T+m}^*= \hat{\boldsymbol{y}}_{ T+ m} + \hat{\boldsymbol{\varepsilon}}_{T}$.  The \emph{one-off} adjustment considers $\hat{\boldsymbol{y}}_{T+1}^*= \hat{\boldsymbol{y}}_{ T+ 1} + \hat{\boldsymbol{\varepsilon}}_{T}$ and compute $m$-ahead forecasts using $\hat{\boldsymbol{y}}_{T+1}^*$; i.e., they only adjust once. The \emph{simple adjustment} considers only $\hat{\boldsymbol{y}}_{T+m}^*= \hat{\boldsymbol{y}}_{ T+ m} + \hat{\boldsymbol{\varepsilon}}_{T}$. The \emph{tailing-off} adjustment considers
\begin{align*}
  \hat{\boldsymbol{y}}_{T+m}^*
  &=\hat{\boldsymbol{y}}_{T+m} + \sum_{i=0}^m \mathbf{\Pi}^i \mathbf{H}^{m-1-i}  \hat{\boldsymbol{\varepsilon}}_T,
\end{align*}
where $\mathbf{\Pi}$ is the parameter matrix of  the error correction term. It is shown that the forecast bias is reduced  when the long-run relationship of VECM changes. \\

It is important to note that their method uses $\hat{\boldsymbol{\varepsilon}}_{T}$. In other words, the hope of reducing forecast risk depends on whether a large deviation is observed at $t=T$. That is, the method is not immune to unprecedented and unobserved shock.

\textbf{Summary of \cite{castle2015robust}:} \cite{castle2015robust} proposed a number of robust forecasting in contrast to equilibrium-correction models. However, their proposed methods would depend on whether past data contain future shock signal to adjust for the forecast. As a result, similar to \cite{clements1996intercept}, it is not robust to unprecedented and unobserved shock. \\

\textbf{Summary of \cite{tsay1986time}:} \cite{tsay1986time} specifies a general generating  mechanism of outliers and corresponding outlier detection methods for ARMA model. The two types of his proposed outlier generating mechanism are innovational outlier and additive outlier. The additive outlier only affects observation at $t= T_0$ for some $T_0 \in \{ 1, \ldots, T\}$. In contrast, the innovational outlier introduces a disturbance on the white noise so that it influences the entire process and impacts future values. In our study, in our AR(1) example,  the unprecedented shock is similar to innovational outlier in the sense that the contaminated response will impact future values through autoregressive structure. However, the difference is that the shock is an additive effect.

@@

@@

In our setup, we only model the time series under study up to $t = 1, \ldots, T_1^*+1$.  We do not know what happened  after $T_1^*+1$. Under our setup, there are two possible situations. First, there is no shock after $T_1^*+1$. Second, there are $k$ shocks after $T_1^*$, say, at $T_1^*+d_1, \ldots, T_1^* + d_k$. \\

@@

As we talked above, there are two situations. When there is no shock after $T_1^*+1$, we can simply use standard forecast for $m$-ahead  prediction in time series methodologies. When there are $k$ shocks after $T_1^*$, in our method, one should construct  $k$ additional donor pools to estimate the $k$ arriving shock effects. The details are provided in the Discussion Section in the revised manuscript. \\

Suppose that  the existing donor pool has time series that experience $k$ shocks, each of which is similar to the one the time series under study are going to. Then, we can readily apply the above stated method to estimate the \emph{shock transition} and adjust for the forecasts.\\

@@

In fact, it is more of a modeling assumption. If we assume an AR model, the impact of any shock will diminish as time passes by. However, if we assume an additive model, the impact will be permanent.

@@

To our best knowledge, our theoretical results are not related to when the transitory shocks die out. In our proposition, the risk reduction does not depend on the autoregressive parameter $\phi_1$, which controls the rate how the impact of the shock dies out. Our proposition is related to the adjustment at time point $T_1^*+1$ but not in a dynamic fashion.
} \\

@@

Lastly,  greater number of bootstrap replication $B$ is preferred. Usually, $B = 200$ is sufficient. Ideally, $k=n$ is preferred. However, if the data size is large such that $k=n$ is computationally expensive, we found that $k = 5$ or $k = 10$ works well. In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool. } \\

>>>>

\response{Thanks for pointing it out. The discussion of those papers is included in the introduction section of the revised manuscript.}\\

@@

\response{The simulation presents the results  for a range of series. To generate confidence of our proposed approach, we will include another data example of forecasting the stock price of Apple Inc. during MacBook release to illustrate our methods.}

@@

Thank you for your appreciation of the potential of our methods, and for your valuable detailed comments.  We think these comments will help a lot in improving our manuscript.\\

@@

In our setup, we only model the time series under study up to $t = 1, \ldots, T_1^*+1$.  We do not know what happened  after $T_1^*+1$. Under our setup, there are two possible situations.  First, there is no shock after $T_1^*+1$. If we assume an AR structure, the impact of the shock should decade along time. If we assume an additive structure without autoregressive component, the shock will be permanent.  Second, there are $k$ shocks after $T_1^*$, say, at $T_1^*+d_1, \ldots, T_1^* + d_k$. \\

@@

It is theoretically possible but the theoretical justification is left for future research. We will illustrate the idea as follows. \\

Suppose that we are interested in estimating shock transition of the time series of interest for $d$ periods for time points, say, $T_1^* +1, \ldots, T_1^*+d$. Assume also that $T_i^* + d \leq T_i$ for $i = 2, \ldots, n+1$.  We can use existing change-point detection methods to identify multiple change-points such that we can generate a change-point vector $\mathbf{D}_i = (D_{i, T_i^*+1}, \ldots, D_{i, T_i^*+d})^{T}$, where $D_{i, T_i^*+j}=1$ if there is a change-point (i.e., a shock) occurring at $t=T_i^*+j$.  Or, $\mathbf{D}_i$ can be given by the user simply. Next, we can  estimate the shock effect using OLS at which $D_{i, T_i^*+j}=1$ for $j = 1, \ldots, d$. Then, we can obtain $\hat{\mathbf{S}}_i$ that is a vector with $j$th entries being $0$ if there is no shock at $T_i ^ * + j$ but being the estimated shock effect  if there is. \\

Suppose we have covariates of the time series of interest up to $T_1^* +d$. Then, we can construct similar synthetic control weights  $\mathbf{W}^*$ as illustrated in the manuscript. Or, a more careful construction of synthetic control weighting is needed since we usually do not have the covariates up to $T_1^*+d$ in practice for $d$ being large. We leave it for future research. Then, we compute
\begin{align*}
  \hat{\mathbf{S}}_1 = \sum_{i=2}^{n+1} w_i^* \hat{\mathbf{S}}_i 
\end{align*}
as the estimated shock transition. However, it cannot be a simple intercept correction dummy because shock effects in $\hat{\mathbf{S}}_1$ should be considered in the $m$-ahead forecasts if we are interested in time series forecasts. For example, in computing $\hat{y}_{1, T_1^*+2}$ when there is no shock effect at $T_1^*+2$, we need to consider the adjusted forecast  $\hat{y}^2_{1, T_1^*+1}=\hat{y}^1_{1, T_1^*+1} + \hat{\alpha}_1$.
\\

@@

If all the time series in the donor pool experience more than one shock, it would be hard to judge whether the shock is anticipated to be permanent or transitory. It is because more than two sources of shocks exist.\\

If all the time series in the donor pool experience  only experience one shock, it is possible to do such anticipation. We will illustrate the idea as below. \\

Consider the model
\begin{align*}
  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i, t} + \beta_i I( t\leq T_i^*)+ \varepsilon_{i,t}.
\end{align*}
Note that we consider a general model  but not AR($p$) because the shock in AR($p$)  must be transitory due to weakly stationarity assumption. If we assume $\varepsilon_{i,t} \sim N(0,1)$ i.i.d., we can estimate $\beta_i$ using OLS.  Using the weights $\mathbf{W}^*$ from previous procedure, we can  compute
\begin{align*}
  \hat{\beta}_1 = \sum_{i=2}^{n+1} w_i^* \hat{\beta}_i
\end{align*}
If $\hat{\beta}_1$ is close to 0, the shock is anticipated to be transitory. Otherwise, it is anticipated to be permanent. However, a threshold is needed. One can use bootstrap to estimate the distribution of   $\hat{\beta}_1$ and conduct hypothesis testing to test $H_0: E(\hat{\beta}_1)=0$ versus $H_1: E(\hat{\beta}_1)\neq 0$. \\

@@

To our best knowledge, we haven't established the rigor of the above idea and do not know whether the theoretical statements can adapt to when transitory shocks die  out.} \\

@@

Lastly,  greater number of bootstrap replication $B$ is preferred. Usually, $B = 200$ is sufficient. Ideally, $k=n$ is preferred. However, if the data size is large such that $k=n$ is computationally expensive, we found that $k = 5$ or $k = 10$ works well. In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool. \\

We include these comments at the end of Section 3 and Section 4 of the revised manuscript.} \\

### 2020-12-31 Revision/manuscript.tex
revised comments and manuscript with addition of Section 5.2 for apple example

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. In this setting, the additive shock effect is a random effect that is parameterized in the autoregressive model. The shock effect is then estimated using ordinary least squares (OLS). The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects from outside data sources are all thought to arise from a  data generating process similar to that of the shock under study. For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.

@@

We estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed. We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest. This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest. Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}. The context in \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}. In our context, the yet to be observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the time series forming the donor pool.

@@

\begin{figure*}[t!]
  \begin{center}
    \subfloat[]{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
     \subfloat[]{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
  \end{center}
     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$. (a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series. (b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.  The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool. \textcolor{red}{$\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with. In this example,
    they differ only by an adjustment $\hat{\alpha}=10.22$.} It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
\end{figure*}

@@

Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$. \textcolor{red}{In this article, we consider a  special case that the model includes random effects for the covariates, autoregressive structure, and an additional shock effect, whose presence or absence is given by the indicator variable $D_{i,t}$.  We will assume that the donor pool time series are independent of the time series under study. The details of this model are in the next section.}

@@

@@

\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
\begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
\end{align*}
\item Under $\mc{M}_{22}$, 
\begin{align*}
\var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
\end{enumerate}
Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, \textcolor{red}{where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}}.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.

@@

\section{Forecasting Conoco Phillips stock in the presence of shocks}
\label{forecasting}

@@

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG2.pdf}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. \textcolor{red}{Black dots and magenta line represent real data and fitted line, respectively.}}
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

@@

\textcolor{red}{We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$. Without loss of generality, we assume $m = 2$. There are two cases. First, suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. Second, assume that the time series under study will experience a shock at $T_1^* + 2$, say $\alpha_1^{(2)}$.  Under our framework, users may want to construct another set of donor pool with time series that experience shock similar to  $\alpha_1^{(2)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(2)}$.  The forecast at $t = T_1^* + 2$ is
\begin{align*}
  \hat{y}^2_{1, T_1^*+2}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +2} + \hat{\alpha}_1^{(2)},
\end{align*} 
where $\hat{y}_{1, T_1^* + 1}^2$ is defined as in Section \ref{forecast}. These two cases can be generalized to  forecasting $m\geq 2$ more periods. The scenarios for forecasting in AR($p$), or other general models are analogous.}

\textcolor{red}{In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$. The methodology can be extended to more general timing scenarios. Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.}

>>>>

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. In this setting, the additive shock effect is a random effect that is parameterized in the autoregressive model. The shock effect is then estimated using ordinary least squares (OLS). The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects from outside data sources are all thought to arise from a  data generating process similar to that of the shock under study. For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks. \textcolor{red}{Our shock effect setting is also similar to the data generating mechanism of  \cite{tsay1986time} studied for ARMA model. \cite{tsay1986time} studied additive outliers that contaminates on the data at only one or multiple specific points but not others, and innovational outliers that impact the subsequent responses. Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}

@@

We estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed. We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest. This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest. \textcolor{red}{Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts. However, the approach of \cite{clements1996intercept} is not robust to unprecedented and unobserved shock since the shock signal is not embedded in the data. \textcolor{red}{Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust approaches for forecasting vector equilibrium-correction models but their forecast requires  conditioning on  the past data that contain shock signal, and thus not robust under our setting.}}

Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}. The context in \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}. In our context, the yet to be observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the time series forming the donor pool.

@@

\begin{figure*}[t!]
  \begin{center}
    \subfloat[]{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
     \subfloat[]{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
  \end{center}
     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$. (a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series. (b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.  The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool. $\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with. In this example,
    they differ only by an adjustment $\hat{\alpha}=10.22$. It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
\end{figure*}

@@

Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$. In this article, we consider a  special case that the model includes random effects for the covariates, autoregressive structure, and an additional shock effect, whose presence or absence is given by the indicator variable $D_{i,t}$.  We will assume that the donor pool time series are independent of the time series under study. The details of this model are in the next section.

@@

\textcolor{red}{At the end, we provide some preferred user decisions for usage of shock-effect estimators. First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution. Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool. Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.}

@@

\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
\begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
\end{align*}
\item Under $\mc{M}_{22}$, 
\begin{align*}
\var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
\end{enumerate}
Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.

@@

\textcolor{red}{In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is believed to be large. If $p < n$ and non-uniqueness problem is of concern due to theoretical reasons,  $\mathcal{B}_f$ is preferred. In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.}

\section{Empirical examples}

\textcolor{red}{In this section, we discuss two data examples of post-shock prediction. Section \ref{forecasting} discusses the prediction of Conoco Phillips stock under the oil supply shock and financial crisis shock. Complementary to Section \ref{forecasting}, we further apply our proposed method to forecasting Apple stock price with shock source from releasing MacBook series product.}

\subsection{Forecasting Conoco Phillips stock in the presence of shocks}
\label{forecasting}

@@

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG2.pdf}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. Black dots and magenta line represent real data and fitted line, respectively.}
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

\subsection{Forecasting Apple stock in the presence of shocks}

Apple Inc. is an American technology company that develops a range of electronics and software with typical products, such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Mac sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Mac account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. near the release of MacBook series on November, 10th, 2020. In particular, in recent years, we observe that it usually takes two or more than two days for the shock to take effect on the stock price in the case of Apple Inc. Therefore, different from Section \ref{forecasting}, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.} Similar to Section \ref{forecasting}, we use an AR(1) model to forecast the stock price of Apple Inc. We consider 20 trading days data for the time series of interest and time series in the donor pool. Likewise, all the estimates will be adjusted for inflation. Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$ in replace of the one in Section \ref{modelsetup}. As a result, a generalized weighting of Section \ref{constructionofestimators} is used. To be specific, we mean 
  \begin{align*}
    \mathbf{X}_1 = \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \quad \text{ and } \quad 
    \mathbf{X}= \begin{pmatrix}
      \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
    \end{pmatrix},
  \end{align*}
  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ stands for the covariates from time $t = T_i^* +1$ to $t = T_i^*+2$. The model $\mc{M}_2$ is then generalized to 
  \begin{align*}
    \mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
\end{array}
  \end{align*}
  where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
  \item \textbf{Selection of covariates.} Different to Section \ref{forecasting}, we consider only  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select AR(3) for S\&P 500 index prices and AR(1)  for 13 Week treasury bill rates. We used Ljung-Box tests to test for model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. Then, we use 2-ahead forecasts to predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date as  in the middle of 20 trading days for 2017, 2018, and 2019.  The shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively. Those dates are the past dates when Apple introduced new series of MacBook products in the corresponding year.
\end{enumerate}

The covariates and response of time series in the donor pool are adjusted for inflation. The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively. Using  the same treatment of the covariates in computing $\mathbf{W}^*$ as in Section \ref{forecasting}, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.673.
$ It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.

The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 0.966$, $\hat{\alpha}_{\rm wadj}=0.950$, and $\hat{\alpha}_{\rm IVW} = 0.955$. The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.183$, $0.084$, and $0.085$, respectively. Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk.

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG3.pdf}
    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and magenta line represent real data and fitted line, respectively.}
    \label{Fig3}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

As we can see from Figure \ref{Fig3}, the post-shock forecasts perform nearly perfectly. The unadjusted forecast misses the post-shock by 0.919 dollars. The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.047, 0.035, and 0.031 dollars. In other words, the true shock effect is nearly fully recovered by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$. It implies that the construction of donor pool is successful. To explain, it appears as a trend that in recent 3 years, Apple inc. only updates the hardware of the MacBook series in the release of every year without much redesign, and improves the their hardware performance significantly \citep{apple2017, apple2018, apple2019} . It is the case for the release in 2020 as well. The new MacBook series consider M1 chip invented by Apple inc. itself in replace of chips by Intel inc. in the past years, and their CPU speed improves significantly; the M1 chip enables  Mac users to use the apps developed in iPhone and thus run a greater range of applications than before \citep{apple2020}. Therefore, in this example, our analysis is similar to \cite{baumeister2014real} in that the  forecast is conditioned on past shocks and the shock is within the range of historical experience.

@@

We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$. Without loss of generality, we assume $m = 2$. There are two cases. First, suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. Second, assume that the time series under study will experience a shock at $T_1^* + 2$, say $\alpha_1^{(2)}$.  Under our framework, users may want to construct another set of donor pool with time series that experience shock similar to  $\alpha_1^{(2)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(2)}$.  The forecast at $t = T_1^* + 2$ is
\begin{align*}
  \hat{y}^2_{1, T_1^*+2}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +2} + \hat{\alpha}_1^{(2)},
\end{align*} 
where $\hat{y}_{1, T_1^* + 1}^2$ is defined as in Section \ref{forecast}. These two cases can be generalized to  forecasting $m\geq 2$ more periods. The scenarios for forecasting in AR($p$), or other general models are analogous.

In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$. The methodology can be extended to more general timing scenarios. Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.
